The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-18 src/static/authors.tex
altaffil coco
fix tom a affil
Apply suggestions from code review
Co-authored-by: Volodymyr <volodymyrss@users.noreply.github.com>
authorlist minor fixes
more tweaks to author list formatting
updated flagged affiliations

\newcommand{\affstsci}{
    Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
}
\newcommand{\affcca}{
    Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
}
\newcommand{\affcfa}{
    Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA, 02138, USA
}
\newcommand{\affbaeri}{
    Bay Area Environmental Research Institute, P.O. Box 25, Moffett Field, CA 94035, USA
}
\newcommand{\affprinceton}{
    Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA
}
\newcommand{\affaperio}{
    Aperio Software Ltd., Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK
}
\newcommand{\afftorontoastro}{
    David A. Dunlap Department of Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto ON M5S 3H4, Canada
}
\newcommand{\affipac}{
    IPAC, MC 100-22, Caltech, 1200E. California Blvd. Pasadena, CA 91125
}

% Paper coordinators, ordered by contributions:
\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\affiliation{\affcca}

@@

%FLAG
\author[0000-0003-1714-7415]{Nicholas~Earl}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green St., Urbana, IL 61801 USA}

@@

\author[0000-0002-9599-310X]{Erik~Tollerud}
\affiliation{\affstsci}

@@

%FLAG
\author{Bruce~Merry}
\affiliation{South African Radio Astronomy Observatory}

@@

\author[0000-0003-4243-2840]{H.~Moritz~G\"{u}nther}
\affiliation{MIT Kavli Institute for Astrophysics and Space Research, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}

% ----------------------------------------------------------------------------
% All others, alphabetical:
\author{Thomas~L.~Aldcroft}
\affiliation{}

@@

%FLAG
\author[0000-0001-7699-3983]{Juanjo~Baz{\'a}n}
\affiliation{CIEMAT, Astroparticle physics, Madrid, Spain.}

%FLAG
\author{Manish~Biswas}
\affiliation{Savitribai phule pune university}

@@

%FLAG
\author[0000-0001-7988-8919]{Matthew~W.~Craig}
\affiliation{Minnesota State University Moorhead}

@@

\author[0000-0002-1821-0650]{Kelle~L.~Cruz}
\affiliation{Hunter College, Physics and Astronomy, 695 Park Avenue, New York, NY 10065}
\affiliation{American Museum of Natural History, Astrophysics, Central Park West at 79th St, New York, NY 10024}
\affiliation{Flatiron Institute, 162 Fifth Avenue, New York, NY 10010}

@@

%FLAG
\author[0000-0002-8919-079X]{Leonardo~Ferreira}
\affiliation{University of Nottingham}

@@

%FLAG
\author{Steve~Guest}
\affiliation{RAL Space}

%FLAG
\author[0000-0001-5848-4077]{Sebastian~Gurovich}
\affiliation{IATE-OAC-UNC}

@@

%FLAG
\author[0000-0002-8646-8362]{Zac~Hatfield-Dodds}
\affiliation{Australian National University, Canberra, Australia}

@@

\author[0000-0002-0832-2974]{Griffin~Hosseinzadeh}
\affiliation{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA}

@@

%FLAG
\author[0000-0002-0629-3006]{Craig~K~Jones}
\affiliation{The Malone Center for Healthcare in Engineering, Johns Hopkins University}

@@

%FLAG
\author[0000-0002-4245-2318]{Chun~Ly}
\affiliation{University of Arizona}

%FLAG
\author[0000-0003-3270-6844]{Zhiyuan~Ma}
\affiliation{University of Massachusetts Amherst}

@@

%FLAG
\author[0000-0001-8100-9514]{Jakob~~M.~Maljaars}
\affiliation{Science \& Technology Corporation}

@@

%FLAG
\author[0000-0003-4189-3450]{Henrik~Norman}
\affiliation{Winter Way, Lerum, Sweden}

@@

%FLAG
\author[0000-0002-5923-4966]{Rohit~R~Patil}
\affiliation{Syracuse University, Syracuse, NY}

@@

%FLAG
\author[0000-0002-9427-5448]{Timothy~E~Pickering}
\affiliation{MMT Observatory}

@@

%FLAG
\author[0000-0002-9523-5640]{Parikshit~Sakurikar}
\affiliation{International Institute of Information Technology - Hyderabad}

%FLAG
\author[0000-0002-3680-4364]{Jes\'us~Salgado}
\affiliation{SKAO Observatory, Jodrell Bank, Cheshire, UK}

@@

\author[0000-0003-2657-3889]{Nicholas~Saunders}
\affiliation{Institute for Astronomy, University of Hawaiʻi at M\=anoa, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{American Museum of Natural History, 200 Central Park West, Manhattan, NY 10024, USA}
\altaffiliation{NSF Graduate Research Fellow}

%FLAG
\author[0000-0001-6353-0808]{Volodymyr~Savchenko}
\affiliation{University of Geneva, Department of Astronomy}

@@

%FLAG
\author[0000-0001-9268-3803]{Gyanendra~Shukla}
\affiliation{Maulana Azad National Institute Of Technology, Bhopal}

@@

%FLAG
\author[0000-0002-9583-263X]{Chen~ZHANG}
\affiliation{Purple Mountain Observatory, CAS}

@@

>>>>

\newcommand{\affstsci}{
    Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
}
\newcommand{\affcca}{
    Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
}
\newcommand{\affcfa}{
    Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA, 02138, USA
}
\newcommand{\affbaeri}{
    Bay Area Environmental Research Institute, P.O. Box 25, Moffett Field, CA 94035, USA
}
\newcommand{\affprinceton}{
    Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA
}
\newcommand{\affaperio}{
    Aperio Software Ltd., Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK
}
\newcommand{\afftorontoastro}{
    David A. Dunlap Department of Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto ON M5S 3H4, Canada
}
\newcommand{\affipac}{
    IPAC, MC 100-22, Caltech, 1200E. California Blvd. Pasadena, CA 91125
}
\newcommand{\affcoco}{
    Astropy Coordination Committee
}
\newcommand{\affsteward}{
    Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson,
    AZ 85721-0065, USA
}

% Paper coordinators, ordered by contributions:
\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\altaffiliation{\affcoco}
\affiliation{\affcca}

@@

\author[0000-0003-1714-7415]{Nicholas~Earl}
\affiliation{Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green St., Urbana, IL 61801 USA}

@@

\author[0000-0002-9599-310X]{Erik~Tollerud}
\altaffiliation{\affcoco}
\affiliation{\affstsci}

@@

\author{Bruce~Merry}
\affiliation{South African Radio Astronomy Observatory, 2 Fir Street, Black River Park, Observatory 7925, South Africa}

@@

\author[0000-0003-4243-2840]{H.~Moritz~G\"{u}nther}
\altaffiliation{\affcoco}
\affiliation{MIT Kavli Institute for Astrophysics and Space Research, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\collaboration{23}{Paper Authors}

% ----------------------------------------------------------------------------
% All others, alphabetical:
\author{Thomas~L.~Aldcroft}
\affiliation{\affcfa}

@@

\author[0000-0001-7699-3983]{Juanjo~Baz{\'a}n}
\affiliation{CIEMAT, Astroparticle physics, Madrid, Spain}

\author{Manish~Biswas}
\affiliation{Savitribai Phule Pune University, Pune, Maharashtra, India}

@@

\author[0000-0001-7988-8919]{Matthew~W.~Craig}
\altaffiliation{\affcoco}
\affiliation{Department of Physics and Astronomy, Minnesota State University Moorhead, Moorhead, MN 56563}

@@

\author[0000-0002-1821-0650]{Kelle~L.~Cruz}
\altaffiliation{\affcoco}
\affiliation{Hunter College, Physics and Astronomy, 695 Park Avenue, New York, NY 10065}
\affiliation{American Museum of Natural History, Astrophysics, Central Park West at 79th St, New York, NY 10024}
\affiliation{Flatiron Institute, 162 Fifth Avenue, New York, NY 10010}

@@

\author[0000-0002-8919-079X]{Leonardo~Ferreira}
\affiliation{Centre for Astronomy and Particle Physics, University of Nottingham, Nottingham, UK}

@@

\author{Steve~Guest}
\affiliation{RAL Space, STFC Rutherford Appleton Laboratory, Harwell, Didcot OX11 0QX, UK}

\author[0000-0001-5848-4077]{Sebastian~Gurovich}
\affiliation{Instituto De Astronom\'{i}a Te\'{o}rica y Experimental -
Observatorio Astron\'{o}mico C\'{o}rdoba (IATE–OAC–UNC–CONICET), C\'{o}rdoba,
Argentina}

@@

\author[0000-0002-8646-8362]{Zac~Hatfield-Dodds}
\affiliation{Australian National University, Canberra, Australia}

@@

\author[0000-0002-0832-2974]{Griffin~Hosseinzadeh}
\affiliation{\affsteward}

@@

\author[0000-0002-0629-3006]{Craig~K.~Jones}
\affiliation{The Malone Center for Healthcare in Engineering, Johns Hopkins University}

@@

\author[0000-0002-4245-2318]{Chun~Ly}
\affiliation{\affsteward}

\author[0000-0003-3270-6844]{Zhiyuan~Ma}
\affiliation{Department of Astronomy, University of Massachusetts - Amherst, 710 North Pleasant Street, Amherst, MA 01003, USA}

@@

\author[0000-0001-8100-9514]{Jakob~M.~Maljaars}
\affiliation{Science \& Technology Corporation, Delft, The Netherlands}

@@

\author[0000-0003-4189-3450]{Henrik~Norman}
\affiliation{Winter Way, Lerum, Sweden}

@@

\author[0000-0002-5923-4966]{Rohit~R.~Patil}
\affiliation{Syracuse University, Syracuse, NY, USA}

@@

\author[0000-0002-9427-5448]{Timothy~E.~Pickering}
\affiliation{MMT Observatory, Tucson, AZ, USA}

@@

\author[0000-0002-9523-5640]{Parikshit~Sakurikar}
\affiliation{International Institute of Information Technology, Hyderabad, India}

\author[0000-0002-3680-4364]{Jes\'us~Salgado}
\affiliation{SKAO Observatory, Jodrell Bank, Cheshire, UK}

@@

\author[0000-0003-2657-3889]{Nicholas~Saunders}
\altaffiliation{NSF Graduate Research Fellow}
\affiliation{Institute for Astronomy, University of Hawaiʻi at M\=anoa, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{American Museum of Natural History, 200 Central Park West, Manhattan, NY 10024, USA}

\author[0000-0001-6353-0808]{Volodymyr~Savchenko}
\affiliation{Department of Astronomy, University of Geneva, Chemin d'\'Ecogia, 16 CH-1290 Versoix, Switzerland}
\affiliation{EPFL SCITAS, Station 9, CH-1015 Lausanne, Switzerland}

@@

\author[0000-0001-9268-3803]{Gyanendra~Shukla}
\affiliation{Maulana Azad National Institute Of Technology, Bhopal, India}

@@

\author[0000-0002-9583-263X]{Chen~ZHANG}
\affiliation{Purple Mountain Observatory, CAS, Qixia District, Nanjing 210023, China}

@@

\collaboration{113}{Astropy Project Contributors}
